### 2017-11-18 README.Rmd
Change fig.path in README.Rmd so output is in tools (#162)
This addresses a CRAN comment and allows CRAN to render the README.md as HTML for their purposes

Closes #160 on upstream
update doi badge

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![DOI](https://zenodo.org/badge/doi/10.5281/zenodo.13131.svg)](http://dx.doi.org/10.5281/zenodo.13131)
[![Build Status](https://api.travis-ci.org/ropensci/RNeXML.png)](https://travis-ci.org/ropensci/RNeXML)

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "tools/README-"
)
```

[![DOI](https://zenodo.org/badge/11856817.svg)](https://zenodo.org/badge/latestdoi/11856817)
[![codecov.io](https://codecov.io/github/ropensci/RNeXML/coverage.svg?branch=master)](https://codecov.io/github/ropensci/RNeXML?branch=master)
[![Build Status](https://api.travis-ci.org/ropensci/RNeXML.png)](https://travis-ci.org/ropensci/RNeXML)
